#Tidy the data

Information as of `r report_date`




##Tidy Title data

Run Tidy on Title

```{r Tidy_Load, dependson = "Import", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

report_date <- params$report_date

# ### 02_Tidy.R ----------------------------------------------------------
#
# This step consists mostly of "non-destructive" data management: assign types
# to columns (factors with correct/human readable levels, dates, etc.),
# correct/censor obviously abnormal values and errors), transform between *long*
# and *wide* format, etc. Useful packages here are `lubridate`, `stringr`, and
# `forcats`.
#
# The results are saved in a **Data/tidy.rds** file.
#
# After this second step, you will have your full data ready to use in R and
# shouldn't have to run the first two steps anymore (unless you get hold of new
# data).

# Load

# read_csv("data/.csv") %>%
# select() %>%
# filter() %>%
# mutate() %>%
# dmap_if(is.character, factor) %>%
#
# #Save the tidy-ed data
# saveRDS(file = "data/tidy.rds")


# Load libraries ----------------------------------------------------------

library(tidyverse)


# Load data and calculate columns -------------------------------------------------

if (!exists("report_date")) {
  report_date <- "2018-06-11"
  }

read_path <- "./data/"
read_name_start <- "D"


# Load data


#D20
die_sides = 20
read_path_name <- paste0(read_path, read_name_start, die_sides, ".csv")
d20 <- read_csv(read_path_name,
                 na = "NA",
                 guess_max = 10000)


#D12
die_sides = 12
read_path_name <- paste0(read_path, read_name_start, die_sides, ".csv")
d12 <- read_csv(read_path_name,
                 na = "NA",
                 guess_max = 10000)


#D10
die_sides = 10
read_path_name <- paste0(read_path, read_name_start, die_sides, ".csv")
d10 <- read_csv(read_path_name,
                 na = "NA",
                 guess_max = 10000)


#D8
die_sides = 8
read_path_name <- paste0(read_path, read_name_start, die_sides, ".csv")
d8 <- read_csv(read_path_name,
                 na = "NA",
                 guess_max = 10000)


#D6
die_sides = 6
read_path_name <- paste0(read_path, read_name_start, die_sides, ".csv")
d6 <- read_csv(read_path_name,
                 na = "NA",
                 guess_max = 10000)


#D4
die_sides = 4
read_path_name <- paste0(read_path, read_name_start, die_sides, ".csv")
d4 <- read_csv(read_path_name,
                 na = "NA",
                 guess_max = 10000)





```





###DataWrangle

Data tidying was handled during Import (dice roll detail values were selected from within a more comprehensive spreadsheet that included summaries and analysis).  Traditional datawrangling was not necessary.


###Tidy - Clean up and print final notes

```{r Tidy_final, dependson = "Tidy_target", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}


#Save the tidy-ed data ----
#D20
die_sides = 20
d20 %>% 
  saveRDS(file = paste0(read_path, read_name_start, die_sides, ".rds"))

#D12
die_sides = 12
d12 %>% 
  saveRDS(file = paste0(read_path, read_name_start, die_sides, ".rds"))

#D10
die_sides = 10
d10 %>% 
  saveRDS(file = paste0(read_path, read_name_start, die_sides, ".rds"))

#D8
die_sides = 8
d8 %>% 
  saveRDS(file = paste0(read_path, read_name_start, die_sides, ".rds"))

#D6
die_sides = 6
d6 %>% 
  saveRDS(file = paste0(read_path, read_name_start, die_sides, ".rds"))

#D4
die_sides = 4
d4 %>% 
  saveRDS(file = paste0(read_path, read_name_start, die_sides, ".rds"))

# rm(list = c("apply_factors",
#             "get_legend",
#             "levels_all",
# 
#             "wrapper",
#             "y_labs"))

# print("02_Tidy")
tidy_warnings <- warnings()


```


Responses were saved as "tidy.rds"


There were **`r length(tidy_warnings)`** warnings during the data tidying.  They were:
`r tidy_warnings` 
