# (PART) Analysis of Title {-}

#Analyze Title

Information as of `r report_date`

##Analysis of Title - \newline subtitle

```{r combined_Load, dependson = "Transform", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Load libraries ----------------------------------------------------------

library(tidyverse)
library(tm)
library(RColorBrewer)
library(wordcloud)
library(gridExtra)
library(ggalluvial)
library(NPS)


# Load Values objects for assignment and filtering ------------------------

source("./Values.R")
source("./functions.R")


# Initialize an empty list to store the results ----
results <- list()


# set parameters & global values ----

output_folder <- "output"

my_fill_color <- brewer.pal(4, "Blues")[3] #for histograms, etc.

#for plots and graphs
my_theme <- theme(
  panel.background = element_blank(),
  axis.line = element_line(size = .5)
)



# Load the transformed data ----

report <- readRDS("data/combined_rolls.rds")

report_names_class <- tibble( "names" = names(report), "class" = map(report, class))

```



##Combined Rolls Analysis - load responses

```{r convert_report_to_combined, dependson = "combined_Load", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Convert report  ------------------------------------------

report_info <- paste0( "results from Title (n = ", nrow(report), ")")
if (report_info != "") {report_info <- paste0( report_info, " ")}

name_token <- "combined"
if (name_token != "") {name_token <- paste0( name_token, "_")}


#special columns that aren't factors by should be included in charts/grapsh, etc.
special_cols <- c( 1:2)

report_names_class %>%
  rownames_to_column() %>%
  mutate(special_cols = rowname %in% special_cols,
         col_num_name = paste0(rowname, " - ", names)
         ) %>%
  filter(special_cols == T) %>%
  .$col_num_name


report_responses_num <- 0
# report_responses_num <- report %>% nrow()

```

**`r report_responses_num`** responses were loaded for analysis.




##Analysis of Dice Rolls


#### Thoughts
* Thoughts go here




#Analysis - Histograms

##Generate Histograms/Bar Charts for all categorical variables (Factors) and select additional columns

```{r combined_Histograms, dependson = "combined_Load", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Histograms -------------------------------------------------

#apply factor levels to all columns that fit within each levels values


#for (i in 122) {
#for (i in 27) {
for (i in 1:ncol(report)) {

  if ( is.factor(report[[i]]) | i %in% special_cols ) {

    x_col <- report %>%
      select(i) %>%
      names(.) %>%
      str_replace_all("/", "")

    x_col_trim <- x_col %>%
      strtrim(25)

    y_lim_max <- report %>%
      count(.[[i]]) %>%
      mutate(max = max(n)) %>%
      count(max) %>%
      .$max * 1.05

    y_breaks <- (y_lim_max / 4 * 1:4) %/% 25 * 25

    x_plot <- report %>%
      ggplot(mapping = aes(x = report[[i]])) +
      geom_bar(fill = my_fill_color) +
      geom_text(stat = "count", aes(label = ..count.., y = ..count..), vjust = -1) +
      scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
      scale_y_continuous(limit = c(0, y_lim_max), breaks = y_breaks) +
      my_theme +
      labs(x = x_col_trim,
          title = wrapper(paste0( i, " - ", x_col, " (n = ", nrow(report), ")"), 90),
          caption = report_info
      )
    # ggsave(paste0(output_folder, "/", name_token, i, "report_histogram_", str_replace_all(x_col_trim, pattern = "/", replacement = ""), ".png"))

    print(x_plot)
    print(paste0( i, " - ", x_col))
  }
}

rm(list = c("x_col",
            "x_col_trim",
            "x_plot",
            "y_breaks" ))

report %>%
  ggplot(mapping = aes(x = rolls)) +
  geom_bar(fill = my_fill_color) +
  facet_wrap(~die, nrow = 3)


```



#Analysis - Chi-Square Tests

```{r combined_pairwise_proportions, dependson = "combined_Load", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# chisq.test -----------------------------------------------

d20 %>% count(D20) %>% .$n
chisq.test(d20 %>% count(D20) %>% .$n)
chisq.test(d12 %>% count(D12) %>% .$n)
chisq.test(d10 %>% count(D10) %>% .$n)
chisq.test(d8 %>% count(D8) %>% .$n)
chisq.test(d6 %>% count(D6) %>% .$n)
chisq.test(d4 %>% count(D4) %>% .$n)

ks.test(d20 %>% count(D20) %>% .$n, runif(2000000, 1, 20))

x <- rnorm(50)
y <- runif(30)
# Do x and y come from the same distribution?
ks.test(x, y)
# Does x come from a shifted gamma distribution with shape 3 and rate 2?
ks.test(x+2, "pgamma", 3, 2) # two-sided, exact
ks.test(x+2, "pgamma", 3, 2, exact = FALSE)
ks.test(x+2, "pgamma", 3, 2, alternative = "gr")
runif(20, 1, 20)
dunif(20, 1, 20)
var(runif(10000))  #- ~ = 1/12 = .08333

```



##Pairwise comparisons of key variables Overall_Satisfaction

```{r combined_pairwise_Overall_Satisfaction, dependson = "combined_Load", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}


# Pairwise by Overall_Satisfaction -----------------------------------------------------------

# plot_calc_pairs(df = report, x = Column, y3 = Overall_Satisfaction, ex_label = '')


```




<!-- Clean up Pairwise calcs ------------------------------------------------- -->

```{r combined_pairwise_clean_up, dependson = "combined_Load", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# 
# # Clean up Pairwise calcs -------------------------------------------------
# 
# rm(list = c("plot_calc_Completed_Quarter",
#             "plot_calc_LTR",
#             "plot_calc_NPS",
#             "plot_calc_OSAT",
#             "plot_calc_Relationship_Officer",
#             "plot_calc_report_Phase",
#             "report_rm"))


```





#Analysis - Clean up and print final notes

```{r combined_final, dependson = "combined_Load", cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# Clean up and print final notes ------------------------------------------

# rm(list = c("i",
#             "j",
#             "my_fill_color",
#             "my_theme",
#             "name_token",
#             "output_folder",
#             ))
# 
# print("04_Analyse")
# warnings()
```



##End